A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-10-22 paper/main.tex
add text for section data availability

\section*{Data availability} \todo[inline]{``This section will be
auto-generated.'' What do we have to do here? I cleaned input datasets
(speechanno and speechanno as subdataset in validation analysis) of this paper
repo from the descriptive nouns}

In addition, released data, code, and manuscript sources are also available on
Github (\url{https://github.com/psychoinformatics-de/studyforrest-paper-speechannotation}).

>>>>

\section*{Data availability}

osf.io: The annotation as both a TSV and TextGrid file as well as scripts and
data of the analysis, doi:
\href{dx.doi.org/10.17605/OSF.IO/GFRME}{10.17605/OSF.IO/GFRME}
